Comment: Reasoning about Interference Between Units

### 2016-06-14 paper/introduction.tex
Version sent to PA for production at first

When we assessed power across many alternative hypotheses in results not shown
here but part of the reproduction archive
for this paper, our intuition was
that the SSR would have more power than the KS test when the outcome was
Normal and when the observational implication of the model of effects would
shift means (i.e.\ the additive model). We used direct simulation of the
randomization distribution to generate $p$-values and repeated that process
1000 times to gauge the proportion of rejections of a range of false
hypotheses  (i.e.\ the power of the tests at many different values of
$\tau_0$). The results bear out this intuition: the SSR has slightly more power than
KS for Normal outcomes in both the additive and multiplicative effects
conditions. SSR has slightly less power than KS when the outcome is skewed for
both models. In general, the SSR ought to be most powerful when the effect of
the experiment involves a shift in the location of the distributions of the
treated versus the controls. And it should be less powerful when the effect of
the experiment is mostly to leave the center of the distribution alone, but,
instead to stretch or compress the tails, or to concentrate the experimental
effect on one quantile.

>>>>

When we assessed power across many alternative hypotheses in results not shown
here but part of the reproduction archive
for this paper \citep{bowers2016dataverse}, our intuition was
that the SSR would have more power than the KS test when the outcome was
Normal and when the observational implication of the model of effects would
shift means (i.e.\ the additive model). We used direct simulation of the
randomization distribution to generate $p$-values and repeated that process
1000 times to gauge the proportion of rejections of a range of false
hypotheses  (i.e.\ the power of the tests at many different values of
$\tau_0$).\footnote{Those interested in the code for this document can find it
at \url{https://github.com/jwbowers/TestStatRIInterference}. } The results bear out this intuition: the SSR has slightly more power than
KS for Normal outcomes in both the additive and multiplicative effects
conditions. SSR has slightly less power than KS when the outcome is skewed for
both models. In general, the SSR ought to be most powerful when the effect of
the experiment involves a shift in the location of the distributions of the
treated versus the controls. And it should be less powerful when the effect of
the experiment is mostly to leave the center of the distribution alone, but,
instead to stretch or compress the tails, or to concentrate the experimental
effect on one quantile.

### 2016-06-14 paper/paper.tex
Version sent to PA for production at first

\author{Jake Bowers \thanks{Associate Professor, Dept of Political Science and Statistics, University of Illinois @ Urbana-Champaign (\texttt{jwbowers@illinois.edu}).} \and Mark Fredrickson \thanks{Ph.D. Student in Statistics and Political Science, University of Illinois @ Urbana-Champaign.} \and Peter M. Aronow \thanks{Assistant Professor, Dept of Political Science and Biostatistics, Yale University}}

>>>>

\author{Jake Bowers \thanks{Associate Professor, Dept of Political Science and
		Statistics, University of Illinois @ Urbana-Champaign
		(\texttt{jwbowers@illinois.edu}). Data and code to reproduce this document
	can be found at \citet{bowers2016dataverse}} \and Mark Fredrickson \thanks{Ph.D. Student in Statistics and Political Science, University of Illinois @ Urbana-Champaign.} \and Peter M. Aronow \thanks{Assistant Professor, Dept of Political Science and Biostatistics, Yale University}}
